TurtleBot SLAM

### 2013-01-23 trunk/Article/Article.tex

\begin{abstract}
 This article describes an implementation of Graph-based Simultaneous Localization And Mapping (Graph SLAM) with frontier-based exploration. The challenge of the SLAM-problem is building a map of the robot's environment and localizing it using uncertain measurement data. Robot localization needs knowledge of the map and vice-versa. Another challenge is to find a strategy to efficiently explore the robot's environment. In the implementation for this article a Graph SLAM algorithm and a Wavefront frontier detection algorithm have been used to achieve both. All the implemented code is first tested and validated in a simulator and later run on a real robot, a TurtleBot. The result is a quickly built map of a sample region.
\end{abstract}

>>>>

\begin{abstract}
 This article describes an implementation of Graph-based Simultaneous Localization And Mapping (Graph SLAM) with frontier-based exploration. The challenge of the SLAM-problem is building a map of the robot's environment and localizing it using uncertain measurement data. Robot localization needs knowledge of the map and vice-versa. Another challenge is finding a strategy to efficiently explore the robot's environment. A Graph SLAM algorithm and a Wavefront frontier detection algorithm have been implemented to solve these problems. This article gives an insight into the implementation process of these algorithms. The implementation is tested and validated in a simulator. The result of the process is a fully explored sample environment.
\end{abstract}
